COG-ED Manuscript

### 2022-01-20 06_Paper/COG-ED/Manuscript.Rmd
1c time and performance hinzugefügt
1c physical funktioniert

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
#apa_table(
#  hypothesis1c_time_contrasts
#  , caption = "Paired contrasts for rmANOVA hypothesis 1c time XXX"
#  , note = "XXX."
#  , escape = TRUE
#)
```

>>>>

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  hypothesis1c_time_contrasts
  , caption = "Paired contrasts for rmANOVA hypothesis 1c time XXX"
  , note = "XXX."
  , escape = TRUE
)
```
